Questioning how Researchers Develop and Present Intrusion Detection Systems

### 2014-09-18 docs/questioning.tex
added number of citations

    \begin{tabular}{l|c|cc|c}

@@

@@

	&& \bf{FP/FN}

@@

	\multirow{13}{*}{Runtime Tainting}
	&   {\it Kiriansky et al.~\cite{KBA02}} & {\bf ?},{\bf ?} & $\sim$1\% & {\it binary code} \\
	&   {\it {\sc cfi}~\cite{ABEL05}} & {\bf ?},{\bf ?} & 0.09--26.78\% & {\it binary code} \\
	&  	{\it SigFree}~\cite{WPLZ10} & \xmark,\xmark & 10\% & {\it binary code} \\
	&  	{\sc csse}~\cite{PB05} & \xmark,\xmark & 2--10\% & {\sc sql} \\
	&  	{\it {\sc lift}}~\cite{QWLKZW06} & \tick,\tick & 6.2\% & {\it binary code} \\ 
	&  	{\it Haldar et al.}~\cite{HCF05} & {\bf ?},{\bf ?} & \xmark & {\sc sql} \\ 
	&  	{\it SecuriFly}~\cite{MLL05} & \xmark,\tick & 9--125\% & {\sc sql}, {\sc xss} \\ 
	&  	{\it Xu et al.}~\cite{XBS06} & \tick,\xmark & 76\% & {\sc sql}, {\sc xss} \\ 
    &  	{\it {\sc wasc}}~\cite{NLC07} & \xmark,\xmark & 30\% & {\sc sql}, {\sc xss} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & \xmark,\xmark & 2.2$\times$ & {\sc sql}, {\sc xss}, {\sc php} \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07} & \xmark,{\bf ?} & {\bf ?} & {\sc xss} \\
	& 	{\it Stock et al.}~\cite{SLMS14} & 0.09\%,\xmark & 7-17\% & {\sc xss} \\

@@

	&  {\it {\sc sql}rand}~\cite{BK04} & {\bf ?},{\bf ?} & 6.5{\it ms} & {\sc sql} \\ 
	&  {\it Noncespaces}~\cite{GC09} & \tick,\tick &  10.3\% & {\sc xss} \\ 
    &  {\it x{\sc js}}~\cite{APKLM10} & \tick,\tick & 1.6--40{\it ms} & {\sc xss} \\

@@

	\multirow{14}{*}{Policy Enforcement}
	&  {\it {\sc dsi}}~\cite{NSS06} & \xmark,\xmark & 1.85\% & {\sc xss} \\ 
	&  {\it BrowserShield}~\cite{RDWDE07} & \tick,\tick & 8\% & {\sc xss} \\ 
	&  {\it Blueprint}~\cite{LV09} & \tick/\tick & 13.6\% & {\sc xss} \\ 
	&  {\it WebJail}~\cite{VDDPJ11} & {\bf ?},{\bf ?} & $\sim$7ms & {\sc xss} \\ 
	&  {\it CoreScript}~\cite{YCIS07} & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
	&  {\it ConScript}~\cite{ML10} & {\bf ?},{\bf ?} & 7\% & {\sc xss} \\
	&  {\it {\sc js}and}~\cite{AVBPDP12} & {\bf ?},{\bf ?} & up to 365\% & {\sc xss}\\
	&  {\it {\sc met}}~\cite{ELX07} & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
    &  {\it {\sc beep}}~\cite{TNH07}  & \tick,\tick & 14.4\% & {\sc xss} \\
	&  {\it {\sc csp}} & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\ 
    &  {\it Google Caja} & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
    &  {\it Phung et al.}~\cite{PSC09} & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\
    &  {\it TreeHouse}~\cite{IW12} & {\bf ?},{\bf ?} & 757–--1218ms & {\sc xss} \\
    &  {\it Dhawan et al.}~\cite{DSG12} & \xmark,{\bf ?} & 16---114\% & {\sc xss} \\

@@

	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & \tick,\tick & {\bf ?} & {\sc sql} \\ 
	&   {\it {\sc didafit}}~\cite{LLW02} & \xmark,\xmark & {\bf ?} & {\sc sql} \\
	&   {\it Valeur et al.}~\cite{VMV05} & 0.37\%,{\bf ?} & 1{\it ms} & {\sc sql} \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\bf ?},{\bf ?} & 3\% & {\sc sql} \\
	& 	{\it Diglossia}~\cite{SMS13} & \xmark,\xmark  & 13\% & {\sc sql}, No{\sc sql} \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09} & \tick,\tick & 39\% & {\sc sql}, {\sc xp}ath \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & \xmark,\xmark  & \xmark & {\sc sql}, {\sc xp}ath \\
	& 	{\it Mattos et al.}~\cite{MSM13} & \tick,{\bf ?} &  {\bf ?} & {\sc xml}, {\sc xp}ath \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & \xmark,\xmark & {\bf ?} & {\sc sql}, {\sc xss} \\
	& 	{\it {\sc swap}}~\cite{WPLKK09} & \tick,\tick & $\sim$180\% & {\sc xss} \\ 
    & 	{\it {\sc xssds}}~\cite{JEP08}  & \xmark,\xmark & {\bf ?} &  {\sc xss} \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & {\bf ?},\xmark & 5---24\% & {\sc xss} \\

>>>>

    \begin{tabular}{l|c|c|cc|c}

@@

	& \bf{\# of Citations}

@@

	&&& \bf{TP,TN,FP,FN}

@@

	\multirow{11}{*}{Runtime Tainting}
%	&   {\it Kiriansky et al.~\cite{KBA02}} & {\bf ?},{\bf ?} & $\sim$1\% & {\it binary code} \\
%	&   {\it {\sc cfi}~\cite{ABEL05}} & {\bf ?},{\bf ?} & 0.09--26.78\% & {\it binary code} \\
	&  	{\it SigFree}~\cite{WPLZ10} & 111 & \xmark,\xmark & 10\% & {\it binary code} \\
	&  	{\sc csse}~\cite{PB05} & 0 & \xmark,\xmark & 2--10\% & {\sc sql} \\
	&  	{\it {\sc lift}}~\cite{QWLKZW06} & 268 & \tick,\tick & 6.2\% & {\it binary code} \\ 
	&  	{\it Haldar et al.}~\cite{HCF05} & 177 & {\bf ?},{\bf ?} & \xmark & {\sc sql} \\ 
	&  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql}, {\sc xss} \\ 
	&  	{\it Xu et al.}~\cite{XBS06} & 297 & \tick,\xmark & 76\% & {\sc sql}, {\sc xss} \\ 
    &  	{\it {\sc wasc}}~\cite{NLC07} & 0 & \xmark,\xmark & 30\% & {\sc sql}, {\sc xss} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 0 & \xmark,\xmark & 2.2$\times$ & {\sc sql}, {\sc xss}, {\sc php} \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & \xmark,{\bf ?} & {\bf ?} & {\sc xss} \\
	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & 0.09\%,\xmark & 7-17\% & {\sc xss} \\
	&   {\it Noxes}~\cite{KJKV09} & 40 & {\bf ?},{\bf ?},{\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\

@@

	&  {\it {\sc sql}rand}~\cite{BK04} & 286 & {\bf ?},{\bf ?} & 6.5{\it ms} & {\sc sql} \\ 
	&  {\it Noncespaces}~\cite{GC09} & 109 & \tick,\tick &  10.3\% & {\sc xss} \\ 
    &  {\it x{\sc js}}~\cite{APKLM10} & 18 & \tick,\tick & 1.6--40{\it ms} & {\sc xss} \\

@@

	\multirow{11}{*}{Policy Enforcement}
	&  {\it {\sc dsi}}~\cite{NSS06} & 135 & \xmark,\xmark & 1.85\% & {\sc xss} \\ 
	&  {\it BrowserShield}~\cite{RDWDE07} & 219 & \tick,\tick & 8\% & {\sc xss} \\ 
	&  {\it Blueprint}~\cite{LV09} & 110 & \tick/\tick & 13.6\% & {\sc xss} \\ 
	&  {\it WebJail}~\cite{VDDPJ11} & 25 & {\bf ?},{\bf ?} & $\sim$7ms & {\sc xss} \\ 
	&  {\it CoreScript}~\cite{YCIS07} & 181 & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
	&  {\it ConScript}~\cite{ML10} & 122 & {\bf ?},{\bf ?} & 7\% & {\sc xss} \\
	&  {\it {\sc js}and}~\cite{AVBPDP12} & 22 & {\bf ?},{\bf ?} & up to 365\% & {\sc xss}\\
	&  {\it {\sc met}}~\cite{ELX07} & 58 & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
    &  {\it {\sc beep}}~\cite{TNH07} & 282 & \tick,\tick & 14.4\% & {\sc xss} \\
	&  {\it {\sc csp}} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\ 
    % &  {\it Google Caja} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
    % &  {\it Phung et al.}~\cite{PSC09} & 75 & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\
    &  {\it TreeHouse}~\cite{IW12} & 18 & {\bf ?},{\bf ?} & 757–--1218ms & {\sc xss} \\
    % &  {\it Dhawan et al.}~\cite{DSG12} & 7 & \xmark,{\bf ?} & 16---114\% & {\sc xss} \\

@@

	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 376 & \tick,\tick & {\bf ?} & {\sc sql} \\ 
	&   {\it {\sc didafit}}~\cite{LLW02} & 85 & \xmark,\xmark & {\bf ?} & {\sc sql} \\
	&   {\it Valeur et al.}~\cite{VMV05} & 226 & 0.37\%,{\bf ?} & 1{\it ms} & {\sc sql} \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & {\bf ?},{\bf ?} & 3\% & {\sc sql} \\
	& 	{\it Diglossia}~\cite{SMS13} & 3 & \xmark,\xmark  & 13\% & {\sc sql}, No{\sc sql} \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09} & 20 & \tick,\tick & 39\% & {\sc sql}, {\sc xp}ath \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 40 & \xmark,\xmark  & \xmark & {\sc sql}, {\sc xp}ath \\
	& 	{\it Mattos et al.}~\cite{MSM13} & 2 & \tick,{\bf ?} &  {\bf ?} & {\sc xml}, {\sc xp}ath \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & \xmark,\xmark & {\bf ?} & {\sc sql}, {\sc xss} \\
	& 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & \tick,\tick & $\sim$180\% & {\sc xss} \\ 
    & 	{\it {\sc xssds}}~\cite{JEP08} & 64 & \xmark,\xmark & {\bf ?} &  {\sc xss} \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & {\bf ?},\xmark & 5---24\% & {\sc xss} \\
